A new type of automated prover based on category theory

### 2022-08-27 paper.tex
double spacing

%% \usepackage[letterpaper, total={5.3in, 9in}]{geometry}	%% set paper size & margin
\usepackage{amsmath}	%% math part 1
\usepackage{flexisym, breqn}	%% math part 2
\usepackage{amssymb, graphics, setspace}	%% math part 3
\usepackage{tikz, tikz-cd}	%% for commutative diagrams
\usepackage{flowchart}	%% for flowchart
\usepackage{float, booktabs}	%% for table & alignment
\usepackage{algorithmicx, algorithm, algpseudocode}	%% for pseudo code composition
\usepackage{blindtext}	%% overfull hbox solution

@@

@@

	\affiliation[1]{organization={Department of Mathematics, College of Sciences, Northerneastern University},city={Shenyang},postcode={110000},country={P.R.China}}
	\affiliation[2]{organization={Northeast Yucai School},addressline={Zhenxing St. 9-5, Heping District},city={Shenyang},postcode={110000},country={P.R.China}}
	%% \maketitle

	\begin{abstract}
	In this article a new type of automated statement proof algorithm based on new data structures, i.e. brackets and map graphs
	and new algorithms is presented. The brackets provide an elegant low-knowledge representation of mathematical concepts. The map graphs offer an efficient machine-learning method which let the computer learn knowledge while proving. Additionally, the new finding is totally built on the category theory. Furthermore, a prototype of the program is given.
	\end{abstract}

@@

	\begin{keyword}
		automatic prover \sep theorem prover \sep algorithm \sep category theory \sep provers \sep statement prover
	\end{keyword}
\end{frontmatter}

>>>>

%% \usepackage[letterpaper, total={5.3in, 9in}]{geometry}	%% set paper size & margin
\usepackage{amsmath}	%% math part 1
\usepackage{flexisym, breqn}	%% math part 2
\usepackage{amssymb, graphics, setspace}	%% math part 3
\usepackage{tikz, tikz-cd}	%% for commutative diagrams
\usepackage{flowchart}	%% for flowchart
\usepackage{float, booktabs}	%% for table & alignment
\usepackage{algorithmicx, algorithm, algpseudocode}	%% for pseudo code composition
\usepackage{blindtext}	%% overfull hbox solution
\usepackage{setspace}	%% double spacing

@@

\doublespacing

@@

	\affiliation[1]{organization={Department of Mathematics, College of Sciences, Northerneastern University},city={Shenyang},postcode={110000},addressline={Department of Mathematics, College of Sciences, Northerneastern University},country={P.R.China}}
	\affiliation[2]{organization={Northeast Yucai School},addressline={Zhenxing St. 9-5, Heping District},city={Shenyang},postcode={110000},country={P.R.China}}
	%% \maketitle

	\begin{abstract}
	In this article a new type of automated statement proof algorithm based on new data structures, i.e. brackets and map graphs
	and new algorithms is presented. The brackets provide an elegant low-knowledge representation of mathematical concepts. The map graphs offer an efficient machine-learning method which let the computer learn knowledge while proving. Additionally, the new finding is totally built on the category theory. Furthermore, a prototype of the program is given. The AMS codes are 03B35, 68V15, 18-00, 18-04, 68W99.
	\end{abstract}

@@

	\begin{keyword}
		automatic prover \sep theorem prover \sep algorithm \sep category theory \sep automatic deduction \sep automatic reasoning
	\end{keyword}
\end{frontmatter}
